Translation Elicitation

### 2021-09-29 Rmd/manuscript.Rmd
Remove big files
Render report

participants <- readRDS(here("Data", "participants.rds"))
stimuli <- readRDS(here("Data", "stimuli.rds"))
responses <- readRDS(here("Data", "responses.rds"))

@@

## Algorithm

## Translation Elicitation task

### Participants

Data collection took place from `r format(min(participants$date), "%dth %B, %Y")` to  `r format(max(participants$date), "%dth %B, %Y")`. We collected data from `r nrow(participants)` participants ($M_{age}$ = `r printnum(mean(participants$age, na.rm = TRUE))`, $SD_{age}$ = `r printnum(sd(participants$age, na.rm = TRUE))`, $Range_{age}$ = `r printnum(min(participants$age, na.rm = TRUE))`-`r printnum(max(participants$age, na.rm = TRUE))`). `r filter(participants, country=="UK") %>% nrow()` participants were British English native speakers living in United Kingdom (`r filter(participants, country=="UK", sex =="Female") %>% nrow()` female), and `r filter(participants, country=="UK") %>% nrow()` participants were Spanish native speakers living in Spain (`r filter(participants, country=="Spain", sex =="Female") %>% nrow()` female). Participants in UK were recruited via Prolific (5£ compensation) and SONA (compensation in academic credits). Participants in Spain were contacted via announcements in Faculties, and were compensated 5€ or an Amazon voucher for the same value. Participants were asked to complete the experiment in a quiet place with good internet connection. We excluded data from participants that a) self-rated their oral and/or written skills in a second or third language as higher than 4 in a 5-point scale (*n* = `r filter(participants, l2oral>4 | l2written>4) %>% nrow()`), b) were diagnosed with a language (*n* = `r filter(participants, impairment) %>% nrow()`)^[We originally planned to exclude participants that reported any visual impairment that glasses would not correct This item was phrased as "Do you have normal or corrected-to-normal VISION? (Yes/No)" in English, and as "¿Tienes problemas de VISIÓN que unas gafas o lentes de contacto NO corrijan? (Sí/No)". However, the proportion of Spanish participants that reported visual impairment was unplausibly large (*n* = `r nrow(filter(participants, country %in% "Spain", vision))`, `r printnum((1-nrow(filter(participants, country %in% "Spain", !vision))/nrow(filter(participants, country=="Spain")))*100)`%). This is possibly due to these participants using glasses dayly and not having read the item until the end, where it is indicated that the use of glasses is considered as normal vision.], or c) did not contribute more than 80% of valid trials (*n* = `r sum(participants$invalid_participant_trials, na.rm = TRUE)`).

### Procedure

The experiment was implemented online using Psychopy/Pavlovia [@peirce2019]. Participants accessed the study from a link provided by Prolific or SONA and completed the experiment from a browser (Chrome or Mozilla). First, participants were informed about the aims of the study and gave informed consent for participating. Second, participants answered a series of questions about their demographic status, their language background, and the set up they were using for completing the study. Third, participants completed the experimental task. Participants were informed that they would listen to a series of pre-recorded words in Catalan or Spanish (English participants) or only Catalan (Spanish participants). They were instructed to listen to each word, guess its meaning in English (English participants) or Spanish (Spanish participants), and type their answer as soon as possible. English participants were randomly assigned to the list of Catalan or Spanish trials. Participants in the Catalan list were presented with `r count(stimuli, group)$n[1]` trials, and participants in the Spanish list were presented with `r count(stimuli, group)$n[2]` trials.

@@

### Stimuli

@@

We divided participants in three groups: English natives tested in Catalan (ENG-CAT), English natives tested in Spanish (ENG-SPA), and Spanish natives tested in Catalan (SPA-CAT). We analysed the accuracy of responses to each item by calculating the proportion of correct responses across participants, resulting in one data point per item and group. We compared how our similarity score fitted the data in comparison with other measures:total shared phonemes, shared phonemic onset, and orthographical Damerau-Levenshtein distance. We fit several Bayesian linear models [@sorensen2015], each including one of the aforementioned variables as predictor, and the proportion of correct responses as output. Continuous predictors were standardised and categorical predictors were sum-coded [@schad2020]. Missing predictor scores were imputed before fitting the models using multiple imputation [@vanbuuren2013]. To test and account for cross-group differences, we included a random intercept for each group. We compared models using leave-one-out cross-validation (LOO, @vehtari2016). More information about the models and model comparison can be found in Appendix X.

>>>>

tar_load(participants)
tar_load(stimuli)
tar_load(responses)
tar_load(model_fits)

@@

## Participants

Data collection took place from `r format(min(participants$date), "%dth %B, %Y")` to  `r format(max(participants$date), "%dth %B, %Y")`. We collected data from `r nrow(participants)` participants ($M_{age}$ = `r printnum(mean(participants$age, na.rm = TRUE))`, $SD_{age}$ = `r printnum(sd(participants$age, na.rm = TRUE))`, $Range_{age}$ = `r printnum(min(participants$age, na.rm = TRUE))`-`r printnum(max(participants$age, na.rm = TRUE))`). `r filter(participants, country=="UK") %>% nrow()` participants were British English native speakers living in United Kingdom (`r filter(participants, country=="UK", sex =="Female") %>% nrow()` female), and `r filter(participants, country=="UK") %>% nrow()` participants were Spanish native speakers living in Spain (`r filter(participants, country=="Spain", sex =="Female") %>% nrow()` female). Participants in UK were recruited via Prolific (5£ compensation) and SONA (compensation in academic credits). Participants in Spain were contacted via announcements in Faculties, and were compensated 5€ or an Amazon voucher for the same value. Participants were asked to complete the experiment in a quiet place with good internet connection. We excluded data from participants that a) self-rated their oral and/or written skills in a second or third language as higher than 4 in a 5-point scale (*n* = `r filter(participants, l2oral>4 | l2written>4) %>% nrow()`), b) were diagnosed with a language (*n* = `r filter(participants, impairment) %>% nrow()`)^[We originally planned to exclude participants that reported any visual impairment that glasses would not correct This item was phrased as "Do you have normal or corrected-to-normal VISION? (Yes/No)" in English, and as "¿Tienes problemas de VISIÓN que unas gafas o lentes de contacto NO corrijan? (Sí/No)". However, the proportion of Spanish participants that reported visual impairment was implausibly large (*n* = `r nrow(filter(participants, country %in% "Spain", vision))`, `r printnum((1-nrow(filter(participants, country %in% "Spain", !vision))/nrow(filter(participants, country=="Spain")))*100)`%). This is possibly due to these participants using glasses dayly and not having read the item until the end, where it is indicated that the use of glasses is considered as normal vision.], or c) did not contribute more than 80% of valid trials (*n* = `r sum(participants$invalid_participant_trials, na.rm = TRUE)`).

## Procedure

The experiment was implemented online using Psychopy/Pavlovia [@peirce2019]. Participants accessed the study from a link provided by Prolific or SONA and completed the experiment from a browser (Chrome or Mozilla). Participants were informed about the aims of the study and gave informed consent for participating. Then, participants answered a series of questions about their demographic status, their language background, and the set up they were using for completing the study. Third, participants completed the experimental task. Participants were informed that they would listen to a series of pre-recorded words in Catalan or Spanish (English participants) or only Catalan (Spanish participants). They were instructed to listen to each word, guess its meaning in English (English participants) or Spanish (Spanish participants), and type their answer as soon as possible. English participants were randomly assigned to the list of Catalan or Spanish trials. Participants in the Catalan list were presented with `r count(stimuli, group)$n[1]` trials, and participants in the Spanish list were presented with `r count(stimuli, group)$n[2]` trials.

@@

## Stimuli

@@

We divided participants in three groups: English natives tested in Catalan (ENG-CAT), English natives tested in Spanish (ENG-SPA), and Spanish natives tested in Catalan (SPA-CAT). We analysed the accuracy of responses to each item by calculating the proportion of correct responses across participants, resulting in one data point per item and group.

We fit several Bayesian linear models [@sorensen2015], each including one of the aforementioned variables as predictor, and the proportion of correct responses as output. Continuous predictors were standardised and categorical predictors were sum-coded [@schad2020]. Missing predictor scores were imputed before fitting the models using multiple imputation [@vanbuuren2013]. To test and account for cross-group differences, we included a random intercept for each group. We compared models using leave-one-out cross-validation (LOO, @vehtari2016). More information about the models and model comparison can be found in Appendix X.

### 2021-09-29 Rmd/report.Rmd
Render report

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = TRUE,
  warning = TRUE, 
  cache.extra = knitr::rand_seed,
  out.width = "100%",
  results = "asis",
  dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
        ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
        ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
        ggplot2.continuous.fill = wesanderson::wes_palettes$Darjeeling1,
        ggplot2.continuous.colour = wesanderson::wes_palettes$Darjeeling1
)

@@

```{r coefs_fixed_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(fit_responses)$fixed %>% 
  as.data.frame() %>%
  rownames_to_column("term") %>% 
  mutate(
    Estimate = ifelse(term=="Intercept", inv_logit_scaled(Estimate), Estimate/4),
    `l-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`l-95% CI`), `l-95% CI`/4),
    `u-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`u-95% CI`), `u-95% CI`/4),
    Est.Error = ifelse(term=="Intercep)", inv_logit_scaled(Est.Error), Est.Error/4)
  ) %>% 
  gt() %>% 
  fmt_percent(2:5) %>% 
  fmt_number(6:6, decimals = 2) %>% 
  fmt_number(7:8, decimals = 0) %>% 
  cols_merge(vars("l-95% CI", "u-95% CI"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    term = md("**Predictor**"),
    Estimate = md("**Mean**"),
    Est.Error = md("**SEM**"),
    "l-95% CI" = md("**95\\% CrI**"),
    Rhat = md("**Rhat**"),
    Bulk_ESS = md("**Bulk ESS**"),
    Tail_ESS = md("**Tail ESS**")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the inverse logit to get the average probability of correct response",
    locations = cells_body(columns = "term", rows = term=="Intercept")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
    locations = cells_body(columns = "term", rows = term %in% c("pthn", "lv", "onset1", "pthn:lv", "pthn:onset1", "lv:onset1", "pthn:lv:onset1"))
  ) %>% 
  tab_footnote(
    footnote = "ESS: Effective sample size",
    locations = cells_column_labels(columns = c("Bulk_ESS", "Tail_ESS"))
  ) %>% 
  cols_align(
    align = c("center"),
    columns = 2:4
  )
```

```{r post_fix, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Points and error bars in indicate the posterior means, and 50% and 95% CrI. The intercept has been transformed using the inverse logit to get the average probability of correct response. The resto of the coefficients has been transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable."}
post <- gather_draws(fit_responses, `b_.*`, regex = TRUE) %>% 
  mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4))

ggplot(post, aes(.value, .variable, fill = .variable)) +
  geom_vline(xintercept = 0) +
  stat_halfeye() +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_fixed.png"))
```

@@

```{r model_comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
map(loo$loos, "estimates") %>% 
  map(function(x){
    as.data.frame(x) %>% 
      rownames_to_column("ic")
  }
  ) %>% 
  bind_rows(.id = "model") %>% 
  clean_names() %>% 
  filter(ic %in% c("elpd_loo", "looic")) %>% 
  pivot_wider(names_from = ic, values_from = c("estimate", "se")) %>% 
  left_join(rownames_to_column(as.data.frame(loo$comparison, "model"))) %>% 
  mutate(formula = c(
    "~ 1 + frequency + (1 | participant)",
    "~ 1 + frequency + pthn + (1 + pthn | participant)",
    "~ 1 + frequency + pthn*vowel_ratio + (1 + pthn*vowel_ratio | participant)",
    "~ 1 + frequency + pthn*consonant_ratio + (1 + pthn*consonant_ratio  | participant)",
    "~ 1 + frequency + pthn*(consonant_ratio + consonant_ratio) + (1 + pthn*(consonant_ratio + consonant_ratio) | participant)"
  )) %>% 
  arrange(desc(model)) %>% 
  select(formula, estimate_elpd_loo, se_elpd_loo, estimate_looic, se_looic, elpd_diff, se_diff) %>%
  rename(model = formula) %>% 
  gt() %>% 
  fmt_number(2:7) %>% 
  cols_merge(c("estimate_elpd_loo", "se_elpd_loo"), pattern = "{1} ({2})") %>% 
  cols_merge(c("estimate_looic", "se_looic"), pattern = "{1} ({2})") %>% 
  cols_merge(c("elpd_diff", "se_diff"), pattern = "{1} ({2})") %>% 
  cols_label(
    model = md("**Model**"),
    estimate_elpd_loo = md("**ELPD<sub>LOO</sub> (SE)**"),
    estimate_looic = md("**LOO-IC (SE)**"),
    elpd_diff = md("**ELPD<sub>diff</sub> (SE)**")

  )

@@

```{r post_re, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
post_re <- gather_draws(fit_responses, r_participant[participant, .param]) %>% 
  mean_qi() %>% 
  ungroup() %>% 
  left_join(select(participants, participant, group)) %>% 
  arrange(group, participant, .param)

@@

m <- add_fitted_draws(nd, fit_responses, n = 50, re_formula = NA) %>% 
  mutate_at(vars(consonant_ratio, vowel_ratio), function(x) paste0(x, " SD"))

ggplot(m, aes(pthn, .value, colour = interaction(consonant_ratio, vowel_ratio, sep = "/"), fill = interaction(consonant_ratio, vowel_ratio, sep = "/"))) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Phon. neigh. dens. (SD)", y = "P(Correct)",
       colour = "Consonant/Vowel similarity", fill = "Consonant/Vowel similarity") +
  scale_y_continuous(labels = scales::percent, limits= c(0, 1)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  ) 
ggsave(here("Figures", "responses_pthn.png"))

@@

m <- add_fitted_draws(nd, fit_responses, n = 50, re_formula = NA) %>% 
  mutate_at(vars(pthn, vowel_ratio), function(x) paste0(x, " SD"))

ggplot(m, aes(consonant_ratio, .value, colour = interaction(vowel_ratio, pthn, sep = "/"), fill = interaction(vowel_ratio, pthn, sep = "/"))) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Consonant similarity", y = "P(Correct)", colour = "PTHN/Vowel similarity",
       fill = "PTHN/Vowel similarity") +
  scale_y_continuous(labels = scales::percent, limits= c(0, 1)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_consonant.png"), height = 4, width = 4.5)

@@

m <- add_fitted_draws(nd, fit_responses, n = 50, re_formula = NA) %>% 
  mutate_at(vars(pthn, consonant_ratio), function(x) paste0(x, " SD"))

ggplot(m, aes(vowel_ratio, .value, colour = interaction(consonant_ratio, pthn, sep = "/"), fill = interaction(consonant_ratio, pthn, sep = "/"))) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Vowel similarity", y = "P(Correct)", colour = "PTHN/Consonant similarity",
       fill = "PTHN/Consonant similarity") +
  scale_y_continuous(labels = scales::percent, limits= c(0, 1)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_vowel.png"), height = 4, width = 4.5)

@@

ggplot(responses_item, aes(reorder(word_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5, colour = "black") +
  geom_errorbar() +
  geom_point(size = 0.5) +
  labs(y = "Correct responses", x = "Word", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "accuracy_item.png"))

@@

ggplot(responses_participant, aes(reorder(participant_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5) +
  geom_errorbar(width = 0.5) +
  geom_point(size = 1) +
  labs(y = "Correct responses", x = "Participant", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "accuracy_participant.png"))

>>>>

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = TRUE,
  warning = TRUE, 
  cache.extra = knitr::rand_seed,
  out.width = "100%",
  results = "asis",
  dev.args = list(png = list(type = "cairo"))
)
options(
  knitr.kable.NA = '-',
  knitr.duplicate.label = "allow",
  ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.continuous.fill = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.continuous.colour = wesanderson::wes_palettes$Darjeeling1
)

@@

```{r coefs_fixed_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(model_fits$fit_4)$fixed %>% 
  as.data.frame() %>%
  rownames_to_column("term") %>% 
  mutate(
    Estimate = ifelse(term=="Intercept", inv_logit_scaled(Estimate), Estimate/4),
    `l-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`l-95% CI`), `l-95% CI`/4),
    `u-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`u-95% CI`), `u-95% CI`/4),
    Est.Error = ifelse(term=="Intercep)", inv_logit_scaled(Est.Error), Est.Error/4)
  ) %>% 
  gt() %>% 
  fmt_percent(2:5) %>% 
  fmt_number(6:6, decimals = 2) %>% 
  fmt_number(7:8, decimals = 0) %>% 
  cols_merge(vars("l-95% CI", "u-95% CI"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    term = md("**Predictor**"),
    Estimate = md("**Mean**"),
    Est.Error = md("**SEM**"),
    "l-95% CI" = md("**95\\% CrI**"),
    Rhat = md("**Rhat**"),
    Bulk_ESS = md("**Bulk ESS**"),
    Tail_ESS = md("**Tail ESS**")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the inverse logit to get the average probability of correct response",
    locations = cells_body(columns = "term", rows = term=="Intercept")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
    locations = cells_body(columns = "term", rows = term %in% c("pthn", "lv", "onset1", "pthn:lv", "pthn:onset1", "lv:onset1", "pthn:lv:onset1"))
  ) %>% 
  tab_footnote(
    footnote = "ESS: Effective sample size",
    locations = cells_column_labels(columns = c("Bulk_ESS", "Tail_ESS"))
  ) %>% 
  cols_align(
    align = c("center"),
    columns = 2:4
  )
```

```{r post_fix, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Points and error bars in indicate the posterior means, and 50% and 95% CrI. The intercept has been transformed using the inverse logit to get the average probability of correct response. The resto of the coefficients has been transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable."}
post <- gather_draws(model_fits$fit_4, `b_.*`, regex = TRUE) %>% 
  mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4))

ggplot(post, aes(.value, .variable, fill = .variable)) +
  geom_vline(xintercept = 0) +
  stat_halfeye() +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

```{r model_comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
model_loos %>% 
  as.data.frame() %>% 
  rownames_to_column("model") %>% 
  arrange(desc(model)) %>% 
  select(model, matches("elpd_loo"), matches("diff")) %>%
  mutate(model = str_replace(model, "fit_", "Model ")) %>% 
  mutate_all(~ifelse(. == 0, NA, .)) %>% 
  gt(rowname_col = "model") %>% 
  fmt_missing(everything(), missing_text = "-") %>% 
  fmt_number(2:5) %>% 
  cols_label(
    model = md("**Model**"),
    elpd_loo = md("**ELPD**"),
    se_elpd_loo = md("***SE***"),
    elpd_diff = md("**diff**"),
    se_diff = md("***SE* diff**")
  )

@@

```{r post_re, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
post_re <- gather_draws(model_fits$fit_4, r_participant[participant, .param]) %>% 
  mean_qi() %>% 
  ungroup() %>% 
  left_join(select(participants, participant, group)) %>% 
  arrange(group, participant, .param)

@@

m <- add_fitted_draws(nd, model_fits$fit_4, n = 50, re_formula = NA) %>% 
  mutate_at(vars(consonant_ratio, vowel_ratio), function(x) paste0(x, " SD"))

ggplot(m, aes(pthn, .value, colour = interaction(consonant_ratio, vowel_ratio, sep = "/"), fill = interaction(consonant_ratio, vowel_ratio, sep = "/"))) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Phon. neigh. dens. (SD)", y = "P(Correct)",
       colour = "Consonant/Vowel similarity", fill = "Consonant/Vowel similarity") +
  scale_y_continuous(labels = scales::percent, limits= c(0, 1)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  )

@@

m <- add_fitted_draws(nd, model_fits$fit_4, n = 50, re_formula = NA) %>% 
  mutate_at(vars(pthn, vowel_ratio), function(x) paste0(x, " SD"))

ggplot(m, aes(consonant_ratio, .value, colour = interaction(vowel_ratio, pthn, sep = "/"), fill = interaction(vowel_ratio, pthn, sep = "/"))) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Consonant similarity", y = "P(Correct)", colour = "PTHN/Vowel similarity",
       fill = "PTHN/Vowel similarity") +
  scale_y_continuous(labels = scales::percent, limits= c(0, 1)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  )

@@

m <- add_fitted_draws(nd, model_fits$fit_4, n = 50, re_formula = NA) %>% 
  mutate_at(vars(pthn, consonant_ratio), function(x) paste0(x, " SD"))

ggplot(m, aes(vowel_ratio, .value, colour = interaction(consonant_ratio, pthn, sep = "/"), fill = interaction(consonant_ratio, pthn, sep = "/"))) +
  stat_lineribbon(.width = 0.95, alpha = 0.25, size = 0) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  labs(x = "Vowel similarity", y = "P(Correct)", colour = "PTHN/Consonant similarity",
       fill = "PTHN/Consonant similarity") +
  scale_y_continuous(labels = scales::percent, limits= c(0, 1)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    panel.grid = element_line(colour = "grey", linetype = "dotted")
  )

@@

ggplot(responses_item, aes(reorder(word_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5, colour = "black") +
  geom_errorbar() +
  geom_point(size = 0.5) +
  labs(y = "Correct responses", x = "Word", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  )

@@

ggplot(responses_participant, aes(reorder(participant_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
  facet_wrap(~group, scales = "free_y") +
  geom_hline(yintercept = 0.5) +
  geom_errorbar(width = 0.5) +
  geom_point(size = 1) +
  labs(y = "Correct responses", x = "Participant", colour = "Group") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 9),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
  )
